CF Registry Analysis

### 2023-06-07 Christine Chan/CF Registry/cf_registry_analysis.qmd
CFRD registry abstract done

---
title: "CF Registry Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
---

```{r}
#| include: false
library(knitr)
library(tidyverse)
library(forestmodel)
library(childsds)
```

@@

Any participants with T1D or T2D were excluded from these analyses. Variables that were entirely missing in a given year (e.g., `A_Vx770` and `A_VX809comb` in 2005) were excluded from those models.

@@

    filter(ReviewYear==year) %>%

@@

           A_supplement_feeding,A_feeding2,

@@

           A_fungalyeast1,A_pulmonarycomplications1,A_mycocultureresults1,
           A_corticosteroids1,cfrd_status_annual,A_Vx770,A_VX809comb)

@@

@@

@@

  df$age_group = cut(df$Age_YrEnd,breaks = c(0,10,18,30,Inf))
  df$age_group = relevel(df$age_group,ref = "(10,18]")

@@

           "A_pulmonarycomplications1","A_mycocultureresults1")

@@

              "A_Vx770","A_VX809comb",bugs)

@@

@@

                                "A_supplement_feeding"))]

@@

@@

  print(forest_model(mod1))

@@

    print(forest_model(mod2))

@@

    print(forest_model(mod3))

@@

    print(forest_model(mod4))

@@

  if("A_mycocultureresults1" %in% colnames(df)){
    mod5 = glm(update(base_mod,.~.+A_mycocultureresults1),data = df,family = "binomial")

@@

    print(forest_model(mod5))

>>>>

---
title: "CF Registry Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
execute:
  echo: false
  warning: false
editor: source
---

```{r}
#| include: false
library(knitr)
library(tidyverse)
library(forestmodel)
library(childsds)
library(labelled)
```

@@

Any participants with T1D or T2D were excluded from these analyses. Variables that were entirely missing in a given year (e.g., `A_Vx770` and `A_VX809comb` in 2005) were excluded from those models. Participants under age 10 at year end were also excluded due to missing PFT data.

@@

    filter(ReviewYear==year,Age_YrEnd >= 10) %>%

@@

           A_supplement_feeding,A_feeding2:A_feeding4,

@@

           A_fungalyeast1,A_pulmonarycomplications1,A_mycocultureresults3,
           A_corticosteroids1,cfrd_status_annual,A_Vx770,A_VX809comb,
           A_hepatobiliary1_3,contains("A_hepatobiliary2_"))

@@

  # Include all kinds of tube feeds

@@

  df$A_feeding3[df$A_supplement_feeding == 0] = 0
  df$A_feeding4[df$A_supplement_feeding == 0] = 0
  df$tube_feeding = 
    apply(df[,c("A_feeding2","A_feeding3","A_feeding4")],1,function(r){
      if(all(is.na(r))){
        return(NA)
      } else {
        return(max(as.numeric(r),na.rm = T))
    })
  # Liver disease
  liver = c("A_hepatobiliary1_3",paste0("A_hepatobiliary2_",1:4))
  df$liver_disease = 
    apply(df[,liver],1,function(r){
      if(all(is.na(r))){
        return(NA)
      } else {
        return(max(as.numeric(r),na.rm = T))
    })

@@

  df$age_group = cut(df$Age_YrEnd,breaks = c(10,18,30,Inf),right = F)
  df$age_group = relevel(df$age_group,ref = "[10,18)")

@@

           "A_pulmonarycomplications1","A_mycocultureresults3")

@@

              "A_Vx770","A_VX809comb",bugs,"tube_feeding","liver_disease")

@@

  df$A_IsOnEnzymes = relevel(df$A_IsOnEnzymes,ref = "Yes")

@@

                                "A_supplement_feeding","A_feeding2","A_feeding3",
                                "A_feeding4","A_FEV1",liver))]

@@

  # Labels
  labels = list(cfrd_status_annual = "CFRD Status",MutClass = "Mutation class",
                Gender = "Sex",A_IsOnEnzymes = "Pancreatic enzyme use",
                A_FEV1_pct_predicted = "FEV1 percent predicted",
                tube_feeding = "Enteric feedings",liver_disease = "Liver disease",
                A_corticosteroids1 = "Use of corticosteroids",
                NumPulmExacerbation = "Admissions for PEx",age_group = "Age group",
                height_perc = "Height percentile",bmi_perc = "BMI percentile",
                A_Vx770 = "Use of CFTR modulator Vx770",
                A_VX809comb = "Use of CFTR modulator Vx809 combination",
                A_pseudomonasaeruginosa = "Pseudomonas aeruginosa",
                A_fungalyeast1 = "Aspergillus (any species)",
                A_pulmonarycomplications1 = "ABPA",
                A_mycocultureresults3 = "Microorganisms in myco culture")
  var_label(df[,vars[which(vars %in% colnames(df))]]) = 
    as.character(labels[vars[which(vars %in% colnames(df))]])
  var_label(df[,bugs[which(bugs %in% colnames(df))]]) = 
    as.character(labels[bugs[which(bugs %in% colnames(df))]])

@@

  print(forest_model(mod1,exclude_infinite_cis = F))

@@

    print(forest_model(mod2,exclude_infinite_cis = F))

@@

    print(forest_model(mod3,exclude_infinite_cis = F))

@@

    print(forest_model(mod4,exclude_infinite_cis = F))

@@

  if("A_mycocultureresults3" %in% colnames(df)){
    mod5 = glm(update(base_mod,.~.+A_mycocultureresults3),data = df,family = "binomial")

@@

    print(forest_model(mod5,exclude_infinite_cis = F))
